Preparing a manuscript for a peer-reviewed journal the FMDL way

### 2021-12-28 IITD_Manuscript.tex
Updated template in response to the latest submissions.

% I am sorry to have to point this out, but you cannot make any changes to the PREAMBLE of this document. It is intentionally designed to keep things generic enough so that this manuscript can be subsequently reformatted to specific journal templates/class files with minimal fuss. For initial submissions, most journals will need just the PDF file (this format) for first round of review. If there is a package you absolutely need to add, you can, but only after ensuring that you cannot live without it. Places in the preamble where you are allowed to make changes are explicitly marked with comments.

\documentclass[12 pt]{article}
% PREAMBLE starts here.

\usepackage[margin=1in,footskip=0.25in]{geometry}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{physics}
\doublespacing
\usepackage{subfigure}
\usepackage{float}
%\usepackage{caption}
\usepackage[version=4]{mhchem}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage{romannum}

\usepackage[backend=biber, isbn=false, url=false, uniquename=init, terseinits=true, hyperref=true, doi=false, style=numeric, defernumbers=false, autocite=plain, sorting=none]{biblatex}
\addbibresource{publishing.bib} % Replace this with the name of your .bib file.
\usepackage[separate-uncertainty = true,multi-part-units=single]{siunitx}
% \renewcommand{\finentrypunct}{
%   \addperiod\space
%   (Cited \arabic{citecounter}~time\ifnumequal{\value{citecounter}}{1}{}{s})%
%  }
\usepackage{hyperref}
%\graphicspath{{./graphics/}} % Add this if needed. Replace graphics with Figures if that is the name of your folder.

@@

% In the title, author and affil directives before, enter your details. Of course, the number of authors and affils can vary - comment out whatever you are not using/add more if needed.

\title{Preparing a manuscript for a peer-reviewed journal the FMDL way}
\author[1]{\small First Author} % ORCID ID of the first author
\author[2]{\small Second Author}  % ORCID ID of the second author
\author[1]{\small Third Author}  % ORCID ID of the third author
\author[1]{\small Postdoc Scholar}  % ORCID ID of the postdoc involved
\author[2]{\small Collaborating PI}  % ORCID ID of the collaborating PI
\author[1]{\small Madhusudan Singh\thanks{msingh@ee.iitd.ac.in}}  % ORCID ID: 0000-0001-5430-1405
\affil[1]{\footnotesize Functional Materials \& Devices Laboratory, Department of Electrical Engineering, IIT Delhi, New Delhi, NCT, India, 110 016.} % Our lab - will remain untouched.
\affil[2]{\footnotesize Department of Chemistry, IIT Delhi, New Delhi, NCT, India, 110 016.} % Change/comment out as needed

@@

% PREAMBLE ends here

@@

@@

As per \href{https://casrai.org/credit/}{CRediT} taxonomy: a) Conceptualization: FA, CP and MS, b) Data curation: FA, SA, TA, and PS, c) Formal analysis: FA and PS, d) Funding acquisition: CP and MS, e) Investigation: FA, SA, TA, and PS, f) Methodology: PS, CP and MS, g) Project administration: PS, CP and MS, h) Resources: CP and MS, i) Software: FA, SA and PS, j) Supervision: PS, CP and MS, k) Validation: FA and TA, l) Visualization: FA, SA, TA, and PS, m) Writing - original draft: FA and SA, n) Writing - review \& editing: FA, CP and MS.

@@

@@

>>>>

% I am sorry to have to point this out, but you cannot make any changes to the PREAMBLE of this document. It is intentionally designed to keep things generic enough so that this manuscript can be subsequently reformatted to specific journal templates/class files with minimal fuss. For initial submissions, most journals will need just the PDF file (this format) for first round of review. If there is a package you absolutely need to add, you can, but only after ensuring that you cannot live without it, and discussing with me. Places in the preamble where you are allowed to make changes are explicitly marked with comments.

% You must run your manuscript through Grammarly prior to sending me the first draft. Not doing so will only lead to waste of your time.

\documentclass[12 pt]{article}
% PREAMBLE starts here. You cannot make any changes until the PREAMBLE ends. It will be marked where it ends.

\usepackage[margin=1in,footskip=0.25in]{geometry}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{textcomp}
\usepackage{gensymb}
\usepackage{physics}
\doublespacing
\usepackage{subfigure}
\usepackage{float}
%\usepackage{caption}
\usepackage[version=4]{mhchem}
\usepackage{amsmath}
\usepackage{authblk}
\usepackage{romannum}
\usepackage{caption} % For Table of Contents entry

\usepackage[backend=biber, isbn=false, url=false, uniquename=init, terseinits=true, hyperref=true, doi=false, style=numeric, defernumbers=false, autocite=plain, sorting=none]{biblatex}
\addbibresource{publishing.bib} % Replace this with the name of your .bib file.
\usepackage[separate-uncertainty = true,multi-part-units=single]{siunitx}
% \renewcommand{\finentrypunct}{
%   \addperiod\space
%   (Cited \arabic{citecounter}~time\ifnumequal{\value{citecounter}}{1}{}{s})%
%  }
\usepackage{hyperref}

@@

% PREAMBLE ends here. You can make changes starting here.

%\graphicspath{{./graphics/}} % Add this if needed. Replace graphics with Figures if that is the name of your folder.

% In the title, author and affil directives before, enter your details. Of course, the number of authors and affils can vary - comment out whatever you are not using/add more if needed. Make sure you enter the ORCID ids for all authors in the comment after each listing below, after ':'.

\title{Preparing a manuscript for a peer-reviewed journal the FMDL way}
\author[1]{\small First Author} % ORCID ID of the first author:
\author[2]{\small Second Author}  % ORCID ID of the second author:
\author[1]{\small Third Author}  % ORCID ID of the third author:
\author[1]{\small Postdoc Scholar}  % ORCID ID of the postdoc involved:
\author[2]{\small Collaborating PI}  % ORCID ID of the collaborating PI:
\author[1]{\small Madhusudan Singh\thanks{msingh@ee.iitd.ac.in}}  % ORCID ID: 0000-0001-5430-1405
\affil[1]{\footnotesize Functional Materials \& Devices Laboratory, Department of Electrical Engineering, IIT Delhi, New Delhi, NCT, India, 110 016.} % Our lab - will remain untouched.
\affil[2]{\footnotesize Department of Chemistry, IIT Delhi, New Delhi, NCT, India, 110 016.} % Change/comment out as needed

@@

@@

\subsection*{Data availability}

Authors will make data available upon reasonable request.

@@

In terms of \href{https://casrai.org/credit/}{CRediT (Contributor Roles Taxonomy)}: a) Conceptualization: FA, CP and MS, b) Data curation: FA, SA, TA, and PS, c) Formal analysis: FA and PS, d) Funding acquisition: CP and MS, e) Investigation: FA, SA, TA, and PS, f) Methodology: PS, CP and MS, g) Project administration: PS, CP and MS, h) Resources: CP and MS, i) Software: FA, SA and PS, j) Supervision: PS, CP and MS, k) Validation: FA and TA, l) Visualization: FA, SA, TA, and PS, m) Writing - original draft: FA and SA, n) Writing - review \& editing: FA, CP and MS.

@@

\subsection*{Author Bios}

% All author photos must be named as XYZbio.png where 'XYZ' are the disambiguated (see below) initials for each author. These must be saved where the rest of your graphics go - the figures subdirectory.
% If you have never written a bio, see mine (below) for an idea of what to include.

\begin{description}
 \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{FA} is a new author when it comes to writing papers. He/she is slowly learning and will get much better with time. % FAbio.png goes here. You should replace the string 'FA' with your own initials. Keep the rest of the filename the same. If there is more than one author with the same initials, use 'FA1', 'FA2' etc.
 \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{SA} is also a new author when it comes to writing papers. He/she is slowly learning and will get much better with time. % SAbio.png goes here.
 \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{TA} is a somewhat seasoned author when it comes to writing papers. He/she is much than when he/she started. % TAbio.png goes here.
 \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{PS} is quite experienced in writing papers. He/she is into teaching younger researchers in how to write a paper. % PSbio.png goes here.
 \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{CP} is our honored colleague, without whose help this work would have never seen the light of the day. He/she is quite busy advising his/her own research group. % CPbio.png goes here.
 \item {\includegraphics[width=1in,height=1.25in,keepaspectratio]{example-image-a}} \textbf{Madhusudan Singh} graduated at the top of his 5-year Integrated M. Sc. Physics class at IIT Kanpur in 1999 with minors in electrical engineering, and computer science. He earned his M. S. degrees in EE and in Mathematics in 2003 and Ph. D. (EE) in 2005 in transport in III-V nitride heterojunctions. After postdoctoral work at MIT in organic optoelectronics, he joined Arizona State University, where he developed printing technologies as a research scientist at the Flexible Display Center. After work on chalcogenide-based flexible electronics at the University of Texas at Dallas, and as an editor at Wiley, he joined the faculty of the Department of Electrical Engineering at IIT Delhi in 2013. His academic service has involved serving as a panel / proposal /application reviewer for the US National Science Foundation (NSF) and the US Department of Energy (DoE), Indian Science \& Engineering Research Board (SERB), Indo-US Science and Technology Forum (IUSSTF), as associate editor of Advanced Functional Materials, in addition to reviewing for several journals, and as editor for special issues for IEEE and IoP. His research interests lie in solution-processed and printed device fabrication methods, flexible electronics, materials and surface chemistry, low cost photovoltaics, solid-state lighting sources, and sensors and detectors. % No change.
\end{description}

@@

\clearpage
\section*{Table of Contents}

% Most good journals require a table of contents entry (this is somewhat discipline and society dependent as well). The purpose of this is an advertisement for your article on the website of the journal. Ordinarily, this will be a separate document, but it is being included here as a separate section so that we can go through drafting of your article without worrying about edits in different files.

\begin{figure*}[!h]
\centering
\includegraphics[width=130mm]{example-image-c}
\captionsetup{labelformat=empty}
\caption{A no more than a 30-words long sentence that summarizes what you did in this paper, written for the benefit of a technically-literate layperson.}
\end{figure*}
